A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-28 paper.tex
Work in progress
Experiment charts upload

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig5_processes_containers .pdf}
    \caption{Life-Cycle algorithm processes in containers comparison.} \label{fig5}
    \end{figure}

@@

Experiment 1: The goal of our first OneMax experiment was to make sure our
Life-Cycle algorithm worked as expected, converging on the solution. For this
experiment, we intentionally used delays (on the tenth of a second magnitude)
to follow the Life-Cycle algorithm behavior on the console output. For this
experiment, we compared the DEAP algorithm versus the Life-Cycle using ten
processes (on containers) where we show the summarized results in Table 2, and
Figure 5 shows their Box and Whisker chart.

Experiment 2: The goal of our second experiment was to confirm the Life-Cycle
algorithm continued working as expected, converging on the solution. For this
experiment, we reduced the time used on delays (now on the thousands of a
second magnitude) to follow the Life-Cycle algorithm behavior. For this
experiment, we only used tournament selection for the reproduction, on the
first configuration running the Life-Cycle on ten processes, versus the second
configuration where we reduced the processes to the minimum basic 5. We show
the summarized results in Table 3, and Figure 6 shows their Box and Whisker
chart.

Experiment 3: The goal of our third experiment was to follow and study the
behavior of the Life-Cycle algorithm that continued converging on the solution.
For this experiment, we remained using minimal delays (thousands of a second
magnitude). For this experiment, we only used tournament selection for the
reproduction, on the first configuration running the Life-Cycle on six
processes, two of whom was the Death stage, versus the second configuration
where we reduced the processes to the minimum (five) but increasing the (Death)
goal approval range to 115. We show the summarized results in Table 4, and
Figure 7 shows their Box and Whisker chart.

Experiment 4: The goal of our fourth and last experiment was to follow and
study the behavior of the Life-Cycle algorithm that continued converging on the
solution. For this experiment, we remained using minimal delays (thousands of a
second magnitude). For this experiment, we compared the OneMax DEAP
implementation versus the Life-Cycle algorithm, only using tournament selection
for the reproduction, with the Life-Cycle configuration running on the minimum
(five) processes but increasing the (Death) goal approval range to 125. We show
the summarized results in Table 5, and Figure 8 shows their Box and Whisker
chart.

>>>>

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig5_processes_containers.pdf}
    \caption{Life-Cycle algorithm processes in containers comparison.} \label{fig5}
    \end{figure}

@@

Experiment 1: The goal of our first OneMax experiment was to make sure our
Life-Cycle algorithm worked as expected, converging on the solution. For this
experiment, we intentionally used delays (on the tenth of a second magnitude)
to follow the Life-Cycle algorithm behavior on the console output. For this
experiment, we compared the DEAP algorithm versus the Life-Cycle using ten
processes (on containers) where we show the summarized results in Table 2, and
Figure 6 shows their Box and Whisker chart.

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig6_experiment01_chart.pdf}
    \caption{Box and Whisker chart for the Experiment 1: OneMax DEAP versus Life-Cycle (10 processes).} \label{fig6}
    \end{figure}

Experiment 2: The goal of our second experiment was to confirm the Life-Cycle
algorithm continued working as expected, converging on the solution. For this
experiment, we reduced the time used on delays (now on the thousands of a
second magnitude) to follow the Life-Cycle algorithm behavior. For this
experiment, we only used tournament selection for the reproduction, on the
first configuration running the Life-Cycle on ten processes, versus the second
configuration where we reduced the processes to the minimum basic 5. We show
the summarized results in Table 3, and Figure 7 shows their Box and Whisker
chart.

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig7_experiment02_chart.pdf}
    \caption{Box and Whisker chart for the Experiment 2: Life-Cycle Tournament selection (10 versus 5 processes).} \label{fig7}
    \end{figure}

Experiment 3: The goal of our third experiment was to follow and study the
behavior of the Life-Cycle algorithm that continued converging on the solution.
For this experiment, we remained using minimal delays (thousands of a second
magnitude). For this experiment, we only used tournament selection for the
reproduction, on the first configuration running the Life-Cycle on six
processes, two of whom was the Death stage, versus the second configuration
where we reduced the processes to the minimum (five) but increasing the (Death)
goal approval range to 115. We show the summarized results in Table 4, and
Figure 8 shows their Box and Whisker chart.

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig8_experiment03_chart.pdf}
    \caption{Box and Whisker chart for the Experiment 3: Life-Cycle Tournament (6 proc. Death x2, versus 5 proc. w/115 goal).} \label{fig8}
    \end{figure}

Experiment 4: The goal of our fourth and last experiment was to follow and
study the behavior of the Life-Cycle algorithm that continued converging on the
solution. For this experiment, we remained using minimal delays (thousands of a
second magnitude). For this experiment, we compared the OneMax DEAP
implementation versus the Life-Cycle algorithm, only using tournament selection
for the reproduction, with the Life-Cycle configuration running on the minimum
(five) processes but increasing the (Death) goal approval range to 125. We show
the summarized results in Table 5, and Figure 9 shows their Box and Whisker
chart.

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig9_experiment4_chart.pdf}
    \caption{Box and Whisker chart for the Experiment 4: OneMax DEAP versus Life-Cycle Tournament (5 proc. w/125 goal).} \label{fig9}
    \end{figure}

The following tables will be removed from the document.
